Manuscript

### 2014-08-31 inst/simulation/manuscript.Rmd
...

context <- Context$new(resultDataDirectory=wd.data.results, processedDataDirectory=wd.data.processed, rawDataDirectory=wd.data.raw, scratchDirectory=wd.scratch, figuresDirectory=wd.figures)
scenarios <- c("A","B","C","D","E","F")
modelNames <- c(paste("SmoothModel", "nbinomial", "matern", "ar1", sep = "-"), paste("SmoothModel", "nbinomial", "ar1", sep = "-"))
iterations <- as.integer(c(1,1,1,1,3,1))

@@

```{r figure-3}
study <- getStudy(scenario="A")
validation <- Validation(study=study)
populationSizes <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)
validation$summarizePopulationSize(populationSizes)

>>>>

context <- Context$new(resultDataDirectory=wd.data.results, processedDataDirectory=wd.data.processed, rawDataDirectory=wd.data.raw, scratchDirectory=wd.scratch, figuresDirectory=wd.figures)
scenarios <- c("A","B","C","D","E","F")
modelNames <- c(paste("SmoothModel", "nbinomial", "matern", "ar1", sep = "-"), paste("SmoothModel", "nbinomial", "ar1", sep = "-"), "FMPModel")
iterations <- as.integer(c(1,1,1,1,3,1))

@@

```{r figure-3}
study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
validation <- Validation(study=study)
populationSizes <- validation$getValidationTemporalPopulationSizes(modelNames=modelNames)
validation$summarizePopulationSize(populationSizes)
